### 2013-10-02 Paper_Markdown.Rmd
Comments & modifications from the CCA analysis of the climate variables structring pollen data.

```{r echo=FALSE, message=FALSE, warning=FALSE}
pol <- mod_pol[,7:ncol(mod_pol)]
clim <- climate[,4:ncol(climate)]

@@

names(clim.ratio) <- colnames(clim)

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}

#  Sakari, can you take a look at this and let me know what you think?
pol <- mod_pol[,7:ncol(mod_pol)]
clim <- climate[,4:ncol(climate)]

@@

names(clim.ratio) <- colnames(clim)
best.clim <- clim.ratio[order(clim.ratio, decreasing = TRUE)]
